\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{fancyhdr}
% \pagestyle{fancy}
\fancyhf{}
\rfoot{\thepage}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\begin{document}

\begin{center}
    \textbf{\Huge Amol Tripathi} \\
    \vspace{0.2em}
    \textbf{8874955991} \quad | \quad 
    \href{mailto:amoltripathi28@gmail.com}{amoltripathi28@gmail.com} \quad | \quad
    \href{https://www.linkedin.com/in/amol-tri12/}{LinkedIn} \quad | \quad \href{https://github.com/amoltrip28}{GitHub}
\end{center}

\section*{EDUCATION}
\textbf{VIT Bhopal University, India} \hfill \textit{June 2022 – June 2026} \\
B.Tech in Computer Science \hfill \textbf{CGPA:} 8.31/10

\section*{TECHNICAL SKILLS}
\textbf{Languages:} Python, C++, C, JavaScript \\
\textbf{Machine Learning:} Supervised & Unsupervised Learning, Deep Learning, Neural Networks, SVM, NLP \\
\textbf{Libraries:} NumPy, Pandas, PyTorch, OpenCV, Matplotlib, Seaborn \\
\textbf{Web:} HTML5, CSS, JavaScript, PHP, Express, Node.js, MySQL, MongoDB, Bootstrap, APIs, Postman \\
\textbf{Tools:} Jupyter, Git, VS Code, MongoDB Compass, MetaMask \\
\textbf{Soft Skills:} Team Leadership, Communication, Project Management

\section*{WORK EXPERIENCE}

\textbf{Project Group Lead, VIT Bhopal} \hfill \textit{Sep 2023 – Feb 2025} \\
\begin{itemize}[leftmargin=1em]
    \item Led a team of 10 in developing an ML model that reduced misclassification by 15\%, optimized training time by 30\%, and improved data processing speed by 40\% using parallel computing techniques.
    \item Developed and deployed a MERN stack-based web application for seamless data visualization and user interaction, improving accessibility and real-time project monitoring.
\end{itemize}


\section*{PROJECTS}
% \textbf{AI-Powered Sentiment Analysis and Tweet Fetching Engine} \hfill \textit{Jan 2025 – Feb 2025} \\
% \textbf{Technologies:} Python, TextBlob, Tweepy, Twitter API v2, NLP \\
% \begin{itemize}[leftmargin=1em]
%     \item Processed 10K+ tweets using Twitter API for real-time sentiment analysis.
%     \item Boosted classification accuracy by 10\% via data preprocessing and polarity scoring.
%     \item Built CLI tool that improved analysis efficiency by 35\%.
% \end{itemize}

\textbf{Foodie Express} \href{https://github.com/amoltrip28/foodie-express}{(GitHub Repo)} \hfill \textit{Jan 2025 – Feb 2025} \\
\textbf{Technologies:} PHP, MySQL, HTML, CSS 
\begin{itemize}[leftmargin=1em]
    \item Developed a hotel food ordering system with database integration and responsive UI, streamlining order tracking for admins and enhancing the guest dining experience.
    \item Applied under-sampling and ensemble techniques to handle class imbalance, resulting in a 15\% improvement in system performance.
\end{itemize}

\textbf{Student Information System (C++)} \href{https://github.com/amoltrip28/Student-Information-System}{(GitHub Repo)} \hfill \textit{May 2023 – June 2023} \\
\textbf{Technologies:} C++, Object-Oriented Programming (OOP), File Handling 
\begin{itemize}[leftmargin=1em]
    \item Developed a console-based student management system in C++ to handle registration, authentication, and record management using modular class-based design.
    \item Implemented file handling for persistent data storage and integrated user authentication with role-based access.
\end{itemize}


\textbf{Breast Cancer Detection Using SVM} \hfill \textit{Jan 2024} \\
\textbf{Technologies:} Scikit-learn, Grid Search, Normalization 
\begin{itemize}[leftmargin=1em]
    \item Achieved 97\% accuracy using SVM with preprocessing and feature scaling on the Wisconsin dataset.
    \item Boosted F1-score with grid search and cross-validation; reduced processing time by 25\%.
\end{itemize}


\section*{ACTIVITIES}

\textbf{Club Participation, VIT Bhopal} \hfill \textit{} 
\begin{itemize}[leftmargin=1em]
    \item Attended various technical and non-technical club activities on campus.
    \item Earned certificates of participation in workshops, coding events, and speaker sessions.
\end{itemize}

\textbf{Hackathon Enthusiast} \hfill \textit{} 
\begin{itemize}[leftmargin=1em]
    \item Participated in multiple college and national-level hackathons.
    \item Collaborated with team members to design and prototype solutions under time constraints.
\end{itemize}


% \section*{CERTIFICATIONS}
% \begin{itemize}[leftmargin=1em]
%     \item Practice Predictive Analysis - FutureSkills Prime Virtual Lab
%     \item Bits and Bytes of Computer Networking – Google (Coursera)
%     \item Cloud Computing – NPTEL (IIT Kharagpur)
%     \item Intro & Intermediate Machine Learning – Kaggle
% \end{itemize}

\end{document}
